Combining bottom up and top down approaches for Drug-Target-Interaction prediction

### 2019-12-08 presentations/2019-12-09/presentation.tex
Complete hmmer compuatation with biggies

\begin{frame}{}

\section{A medium approach to DTI prediction}

>>>>

\section{A medium approach to DTI prediction}
\begin{frame}{How to bring both approaches together?}
	\begin{enumerate}
		\item For each drug, filter possible targets according to protein based measurement
		\item Bring those together with the interaction networks for the prediction
	\end{enumerate}
\end{frame}

\subsection{Filtering possible targets}
\begin{frame}{How to build such a filter?}
	STITCH database got 
	\begin{itemize}
		\item 390 000 chemicals, and
		\item 3.6 million proteins
		\item from over 2000 organisms
	\end{itemize}
	\pause 
	\vspace{0.5cm}
	For each drug, find a motif in the target amino acid sequences and query that against all possible proteins and use the results as features for the prediction
\end{frame}

\begin{frame}{How to find motifs?}
	\begin{enumerate}
		\item Build multi sequence alignment with alignment tool of choice over non-human proteins
			\begin{itemize}
				\item FAMSA, MAFFT, Kalign, MSA Props, Muscle, \dots
			\end{itemize}
		\item Build representation of that alignment
			\begin{itemize}
				\item Hidden Markov model with HMMER
				\item PWM
			\end{itemize}
		\item Query representation against database
	\end{enumerate}
	\pause
	\vspace{0.5cm}
	This is very expensive to compute \dots (10000 hours for alignments of 614 drugs + IBEX queue times for such big jobs)
\end{frame}

\begin{frame}{}
\end{frame}
